---
title: "README"
output: github_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = here::here())
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

pacman::p_load(tidyverse,
               sf)
```

# Article Information

**Tentative title**: Restoration of aquatic habitat complex extends the foraging window of terrestrial consumers

**Authors**: Ibrahim M, Petric R, Wahl C, Terui A

# Analysis Flow

## Aquatic Insect Emergence

Script `analysis_emg_cv.R` runs analysis to calculate temporal CVs.
Data is sourced from `data_raw/data_emg_v_0_2_0.csv`, which was formatted in `format_emg_data.R`.

## Bat Activity Analysis

Script `analysis_bat_gam.R` runs the Generalized Additive Model.
Data is sourced from `data_raw/data_bat.csv`, which was formatted in `format_bat_data.R`.

# Data Sources

## File Description

```{r src}

setwd(str_remove(normalizePath("."), "\\\\rmd"))
source("rmd/table_readme.R")

knitr::kable(df_fnm)
```

## Column Description

```{r column}

options(knitr.kable.NA = "")
knitr::kable(df_cnm)

```

# Session Information

```{r}

source(here::here("code/library.R"))
sessionInfo()

```